\subsection{Football 5-a-side}

\begin{enumerate}

\item Essence of Football 5-a-side
    \begin{itemize}
    \item Football 5-a-side, a sport specifically designed for athletes with visual impairments, is a thrilling and fast-paced game that relies on sound and touch. 
    \item Players, except for the goalkeeper, are blindfolded and use a ball with a bell inside to navigate and score goals. 
    \item The sport showcases exceptional spatial awareness, ball control, and teamwork, as players rely on communication and trust to succeed.
    \end{itemize}

\item Rules, Equipment, and Competition
    \begin{itemize}
    \item Football 5-a-side is played on a smaller field with sideboards to keep the ball in play. 
    \item Each team consists of four outfield players and a sighted goalkeeper. 
    \item The game is played in two 25-minute halves, and players must shout "Voy!" when approaching the ball to avoid collisions. 
    \item The sport utilizes a special ball with a bell and requires players to wear eyeshades to ensure a level playing field.
    \end{itemize}

\item Categories and Classifications
    \begin{itemize}
    \item All outfield players in football 5-a-side are classified as B1, meaning they have very low visual acuity or no light perception. 
    \item The goalkeeper, however, can be fully or partially sighted. 
    \item This classification ensures fair competition and highlights the remarkable skills and adaptations of athletes with visual impairments in navigating and playing the game.
    \end{itemize}

\end{enumerate}