\subsection{Wheelchair Basketball}

\begin{enumerate}

\item Essence of Wheelchair Basketball
    \begin{itemize}
    \item Wheelchair basketball is a fast-paced and exhilarating team sport that showcases the agility, skill, and teamwork of athletes with physical impairments affecting their lower limbs. 
    \item Players maneuver their wheelchairs with precision, dribbling, passing, and shooting the ball to score points against their opponents. 
    \item The sport is a dynamic blend of athleticism, strategy, and sheer determination, captivating audiences with its intensity and excitement.
    \end{itemize}

\item Rules, Equipment, and Competition
    \begin{itemize}
    \item Wheelchair basketball follows the core rules of basketball, with adaptations made for wheelchair users. 
    \item Players compete on a standard basketball court, using specially designed wheelchairs that allow for quick turns and maneuverability. 
    \item The game is played in four 10-minute quarters, and points are scored by shooting the ball through the hoop. 
    \item The sport demands exceptional ball-handling skills, teamwork, and strategic awareness, as players navigate the court and execute plays to outmaneuver their opponents.
    \end{itemize}

\item Categories and Classifications
    \begin{itemize}
    \item Wheelchair basketball utilizes a classification system that evaluates the athlete's functional abilities and assigns them a point value based on their trunk control, sitting balance, and ability to push and maneuver the wheelchair. 
    \item Players are grouped into teams with a maximum total point value, ensuring a balance of abilities on the court. 
    \item This system fosters fair competition and allows athletes with diverse impairments to participate and contribute to their team's success.
    \end{itemize}

\end{enumerate}